Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2017-10-27 paper/main.tex
Clarify some comments

\Chris{For table \ref{table:rnn-throughput} how many layers and what was hidden size?}

@@

@@

\Chris{Put title on Figure \ref{fig:tp_perf}}

@@

\subsection{The Medical Setting}
Medical waveform data consists of long sequences and is a reasonable application area for RNNs.
We applied the GILR-LSTM
on the problem presented in the 2016 PhysioNet/Computing in
Cardiology Challenge 2016.  The aim of the Classification of Normal/Abnormal
Heart Sound Recordings challenge is classify electroencephalogram (EEG) recordings
as coming from a normal or abnormal heart.
The waveforms are recorded on several sets of sensors
and split into a training and testing set. The testing set is not
publicly available, but can be evaluated through a web portal. The top results
cover a large range of techniques, but generally rely on manual featurization of the
raw EEG records. The GILR-LSTM's ability to handle long sequences makes it a
candidate for training directly on the raw EEG signal.
The EEGs are sampled at 2,000 Hz
and range in length from several seconds to more than one hundred seconds,
giving a max sequence length of over 200,000. Since the testing server is not
equipped with a GPU, we cannot run PLR in the inference. We resample the
records to 500 Hz so that we are able to evaluate the test results in a
reasonable amount of time, padding all records that are shorter than the longest.

The training set of data is unbalanced, with 75\% of the data corresponding to
normal hearts. We rebalance the data by oversampling the abnormal data by a factor
of three, including each abnormal heart three times. We train a network feeding
the one dimensional input signal into three stacked GILR-LSTM layers of 16 hidden units each.
Although reasonably small, 16 hidden units allows developing
develop representations. Parallel linear recurrence allows us to rapidly train the network
over the entire long sequence length, so we don't have to work on truncated samples,
downsampled sequenes, or
spend lots of time manually developing EEG specific features.
The model obtained perfect classification on the train dataset after
a few hours \Chris{how many?} of training.
On the unseen test data we obtained a score of PLACEHOLDER.

>>>>

\Eric{For table \ref{table:rnn-throughput} how many layers and what was hidden size?}

@@

\Eric{I think we should delete this section. Already over length limit, doesn't show
anything great}

@@

\Eric{Chris: Put title on Figure \ref{fig:tp_perf}}

@@

\subsection{Abnormal heart sound detection}
Medical waveform data consists of long sequences and is a reasonable application area for RNNs.
We applied the GILR-LSTM
on the problem presented in the 2016 PhysioNet/Computing in
Cardiology Challenge 2016.  The aim of the Classification of Normal/Abnormal
Heart Sound Recordings challenge is classify electroencephalogram (EEG) recordings
as coming from a normal or abnormal heart.
The waveforms are recorded on several sets of sensors
and split into a training and testing set. The testing set is not
publicly available, but can be evaluated through a web portal. The top results
cover a large range of techniques, but generally rely on manual featurization of the
raw EEG records. The GILR-LSTM's ability to handle long sequences makes it a
candidate for training directly on the raw EEG signal.
The EEGs are sampled at 2,000 Hz
and range in length from several seconds to more than one hundred seconds,
giving a max sequence length of over 200,000. Since the testing server is not
equipped with a GPU, we cannot run PLR in the inference. We resample the
records to 500 Hz so that we are able to evaluate the test results in a
reasonable amount of time, padding all records that are shorter than the longest.

The training set of data is unbalanced, with 75\% of the data corresponding to
normal hearts. We rebalance the data by oversampling the abnormal data by a factor
of three, including each abnormal heart three times. We train a network feeding
the one dimensional input signal into three stacked GILR-LSTM layers of 16 hidden units each.
Although reasonably small, 16 hidden units allows developing
develop representations. Parallel linear recurrence allows us to rapidly train the network
over the entire long sequence length, so we don't have to work on truncated samples,
downsampled sequenes, or
spend lots of time manually developing EEG specific features.
The model obtained perfect classification on the train dataset after
a few hours \Eric{how many?} of training.
On the unseen test data we obtained a score of PLACEHOLDER.
